### 2019-01-04 revisions/review-responses.tex

        \question The sentence ``With regard to the nuclear fuel cycle, the 
        thorium cycle produces a reduced quantity of plutonium and minor 
        actinides (MAs) compared to the traditional uranium fuel cycle'' is 
        correct, but the fact that this is an advantage is questionable. The 
        pros\&cons of thorium cycle have been long debated and there is no 
        consensus on its advantage in terms of exposure of workers, exposure of 
        public, geological repository, etc. I would suggest removing the 
        sentence.
        \begin{solution}
                Thanks for your insightful comment. The sentence has been removed.
        \end{solution}

        %---------------------------------------------------------------------

        \question ``Methods listed in references [14, 17, 24, 25, 28, 29, 30] 
        as well as the current work also employ a batch-wise approach''. As a 
        matter of fact, the work in [14]  allows for continuous reprocessing 
        via introduction of ``reprocessing'' time constants. The work from  
        Aufiero (mentioned in the following paragraph) actually used the 
        methodology previously developed in [14]  for verification purposes.
        \begin{solution}
                Thank you for the information. That reference has been removed from the 
                sentence, and following paragraph has been modified to read:

                Accounting for continuous removal or addition presents a 
                greater challenge since it requires adding a term to the 
                Bateman equations. Fiorina \emph{et al.} simulated \gls{MSFR} 
                depletion with continuous fuel salt reprocessing via 
                introducing ``reprocessing'' time constants into the ERANOS 
                transport code \cite{fiorina_investigation_2013}.  The latest 
                SCALE release will also have the same functionality using truly 
                continuous removals \cite{betzler_implementation_2017}.  A 
                similar approach is adopted to model true continuous feeds and 
                removals using the MCNP transport code listed in references 
                \cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.

@@

        \end{solution}

        %---------------------------------------------------------------------

        \question Table 3. It is not clear what ``effective cycle times'' are. 
        Please clarify.
        \begin{solution}
                The ``cycle time'' definition has been added to its first appearance in text.
        \end{solution}

@@

        %---------------------------------------------------------------------

        \question The removal of fission products is made batch wise in the 
        described algorithms. However it is not clear how the fission products 
        with the longest ``effective cycle times'' are removed. Part of them at 
        every batch? Or all of them at the end of the  ``effective cycle 
        times''.  Please clarify. And please clarify the relation between 
        ``effective cycle times'', batches and the average time spent by a 
        fission product in the reactor.
        \begin{solution}
                All of them at the end of the cycle time, and we agree that it
                 was not best solution. Feature improvements in SaltProc are 
                 underway to enable more realistic handling times in the 
                 processing heuristics. To clarify this following paragraph has 
                been added:

                The current version of SaltProc only allows 100\% separation 
                efficiency for either specific elements or groups of elements 
                (e.g. Processing Groups as described in 
                Table~\ref{tab:reprocessing_list}) at the end of the specific 
                cycle time.  This approach works well for fast-removing 
                elements (gases, noble metals, protactinium) which should be 
                removed each depletion step. Unfortunately, for the elements 
                with longer cycle times (i.e. rare earths should be removed 
                every 50 days) this simplified approach leads to oscillatory 
                behavior of all major parameters. In future releases of 
                SaltProc, this drawback will be eliminated by removing elements 
                with longer cycle times using different method: only mass 
                fraction (calculated separately for each reprocessing group) 
                will be removed each depletion step (e.g. 3 days).

@@

        \end{solution}

        %---------------------------------------------------------------------

        \question The oscillatory behavior shown in Fig. 7 on the time scale of 
        months/years is hard to explain. Is this because the fission product 
        with longer residence time are batch-wise removed at their ``effective 
        cycle time''? In case, why not to remove part of them at every depletion 
        step?  
        \begin{solution}
                Yes, the oscillation happened because the fission products 
                with longer residence time are removed at the end of cycle time. We 
                definitely will take your advice and improve the code in future 
                releases. The following text has been added to clarify this issue:

                In fact, SaltProc fully removes all of these elements every 
                3435 days (not a small mass fraction every 3 days) which causes 
                the multiplication factor to jump by approximately 450 pcm, and 
                limits using the batch approach for online reprocessing 
                simulations.  In future versions of SaltProc this drawback will 
                be eliminated by removing elements with longer residence times 
                (seminoble metals, volatile fluorides, Rb, Sr, Cs, Ba, Eu). In 
                that approach, chemistry models will inform separation 
                efficiencies for each reprocessing group and removal will 
                optionally be spread more evenly accross the cycle time.

@@

        \end{solution}

        %---------------------------------------------------------------------

        \question Can the proposed tool adjust reactivity?
        \begin{solution}
                No, and we may someday add this capability, but we expect this 
                will be a challenge outside of the depletion code.
        \end{solution}

@@

        \question ``The main physical principle underlying the reactor 
        temperature feedback is an expansion of material that is heated''. This 
        sentence would deserve some support data. Can you please calculate 
        separately the effect of temperature (Doppler in fuel and spectral 
        shift in graphite) and density?
        \begin{solution}
                Thank you for the excellent recommendation. Effects of temperature
                 and density have been calculated separately and added in Table 5.
                 Moreover, during these simulations we have discovered mistake in 
                 fuel salt and graphite density correlations and completely 
                 recalculated temperature coefficients of reactivity with lower 
                 statistical error. Now initial total temperature coefficient is 
                 closer to the reference and statistical uncertainty was reduced 
                 from 0.046 to 0.038 pcm/K.
        \end{solution}

        %---------------------------------------------------------------------

        \question How uncertainties have been calculated in Table 5? Is this 
        just statistical uncertainty from Serpent calculations? Please clarify
        \begin{solution}
                Yes, uncertainties were determined from statistical error 
                from SERPENT output. Following passage has been added to clarify
                 this point:

                 By propagating the $k_{eff}$  statistical error provided by 
                 SERPENT2, uncertainty for each temperature coefficient was 
                 obtained and appears in Table~\ref{tab:tcoef}. Other sources 
                 of uncertainty are neglected, such as cross section 
                 measurement error and approximations inherent in the equations 
                 of state providing both the salt and graphite density 
                 dependence on temperature.  
        \end{solution}

@@

        %---------------------------------------------------------------------

        \question For calculating the coefficients in table 5, are you only 
        changing densities, or also dimensions? Please clarify and provide a 
        justification.  
        \begin{solution}
        		We have changed both densities and dimensions. This passage 
        		has been modified to read:

                        A new geometry input for SERPENT2, which takes into 
                        account displacement of graphite surfaces, was created 
                        based on this information. For calculation of 
                        displacement, it was assumed that the interface between 
                        the graphite reflector and vessel did not move, and 
                        that the vessel temperature did not change. This is the 
                        most reasonable assumption for the short-term 
                        reactivity effects because inlet salt is cooling 
                        graphite reflector and inner surface of the vessel.

@@

        \end{solution}

        %---------------------------------------------------------------------

        \question ``The fuel temperature coefficient (FTC) is negative for both 
        initial and equilibrium fuel compositions due to thermal Doppler 
        broadening of the resonance capture cross sections in the thorium.'' 
        What is the effect of density?
        \begin{solution}
                This passage has been modified to illuminate the effect of density:

                The fuel temperature coefficient (FTC) is negative for both 
                initial and equilibrium fuel compositions due to thermal 
                Doppler broadening of the resonance capture cross sections in 
                the thorium. A small positive effect of fuel density on 
                reactivity increases from $+1.21$ pcm/K at reactor startup to 
                $+1.66$ pcm/K for equilibrium fuel composition which has 
                a negative effect on FTC magnitude during the reactor operation. 
        \end{solution}

@@

        %---------------------------------------------------------------------

        \question In the manuscript it is not always clear when the authors 
        refer to numerical approximations of physical situations. For instance, 
        the authors write ``Figure 16 demonstrates that batch-wise removal of 
        strong absorbers every 3 days did not necessarily leads to fluctuation 
        in results but rare earth elements 480 removal every 50 days causes an 
        approximately 600 pcm jump in reactivity.'' These 600 pcm are an effect 
        of a numerical approximation, but the way things are presented can be 
        confusing to the reader. Please try to explicitly separate physical and 
        numerical effects. And try to related numerical effects to physical 
        effects. For instance, how does these numerical ``jumps'' affect the 
        results?  In this sense, why the batch-wise removal of strong absorbers 
        every 3 days  was not done? And why a fraction of rare earths  is not 
        removed every three days?
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \question ``The current work results show that a true equilibrium 
        composition cannot exist but balance between strong absorber 
        accumulation and new fissile material production can be achieved to 
        keep the reactor critical.'' Not clear. Do you mean that the equilibrium 
        composition cannot be achieved in a lifetime of the reactor? Please 
        clarify
        \begin{solution}
                This statement, being unclear and misleading, has been removed 
                completely. The intention was to communicate that for a relaxed 
                definition of equillibrium, it can be acheived.
        \end{solution}

@@

        %---------------------------------------------------------------------

        \section*{Reviewer 3}

        \question This paper presents a SaltProc-Serpent2 coupled code system
        to simulate the depletion and online reprocessing process by directly
        changing the isotropic composition of fuel salt. The Molten Salt
        Breeder Reactor (MSBR) was analyzed to demonstrate the simulation
        capability of the developed code system. However, large number of
        similar works have been done and published on this topic. In
        particular, this work is similar with that done by Park et al. with the
        title of ``Whole core analysis of molten salt breeder reactor with
        online fuel reprocessing'' published on ``International Journal of Energy
        Research''. The authors need to prove the uniqueness and innovation
        within their work.
        \begin{solution}
                We appreciate this comment and have made clarifying 
                improvements to indicate the impact of this work throughout the 
                paper. More detail is described regarding these changes in the 
                specific comment responses below.
        \end{solution}

@@

        %--------------------------------------------------------------------

        \question  What are the main differences of this work with the previous 
        works, especially with the work published by Park at al. in ``Whole core 
        analysis of molten salt breeder reactor with online fuel reprocessing''?
        \begin{solution}
                Thank you for your question. The new paragraph has been added:

                The works described in \cite{park_whole_2015} and 
                \cite{jeong_equilibrium_2016} are most similar to the work 
                presented in this paper. However, a few major differences 
                follow: (1) Park \emph{et al.} employed MCNP6 for depletion 
                simulations while this work used SERPENT2; (2) the full-core 
                reactor geometry herein is more detailed 
                \cite{rykhlevskii_full-core_2017}; (3) Park \emph{et al.} and 
                Jeong \emph{et al.} both only considered volatile gas removal, 
                noble metal removal, and $^{233}$Pa separation while the 
                current work implemented the more detailed reprocessing scheme 
                specified in the conceptual \gls{MSBR} design 
                \cite{robertson_conceptual_1971}; (4) the $^{232}$Th neutron 
                capture reaction rate has been investigated to prove advantages 
                of two-region core design; (5) the current work explicitly 
                examines the independent impacts of removing specific fission 
                product groups.
        \end{solution}

@@

        %--------------------------------------------------------------------
        \question  In Page 14, ``depletioncalculations'' should be ``depletion 
        calculations''.
        \begin{solution}
                Thanks for catching this, fixed.
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 21, it looks like the neutron spectrum is not 
        normalized in Figure 10. It is recommended to normalize the neutron 
        spectrum for comparison.
        \begin{solution}
                Thank you for the comment. Neutron energy spectrum in Figure 
                10 and 11 are normalized per unit lethargy and the area under 
                the curve is normalized to 1. The caption has been edited to 
                make this more clear.
        \end{solution}

        %--------------------------------------------------------------------
        \question  In Page 22, ``Figure 13 reflects the normalized power 
        distribution of the MSBR quarter core, which is the same at both the 
        initial and equilibrium states'' contradicts the following statement of 
        ``The spectral shift during reactor operation results in different power 
        fractions at startup and equilibrium''.
        \begin{solution}
                Thanks for catching this. The difference between power fraction
                 is very small that could be seen from Table 4. It is impossible
                  to see the difference in a contour plot that is why we left only 
                 equilibrium composition on Figures 13 and 14. The paragraph has 
                 been modified as follows:

                 Table~4 shows the power fraction in each zone for initial and 
                 equilibrium fuel compositions. Figure~13 reflects the 
                 normalized power distribution of the \gls{MSBR} quarter core 
                 for equilibrium fuel salt composition. For both the initial 
                 and equilibrium compositions, fission primarily occurs in the 
                 center of the core, namely zone I. The spectral shift during 
                 reactor operation results in slightly different power 
                 fractions at startup and equilibrium, but most of the power is 
                 still generated in zone I at equilibrium (table~4).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
